%!TEX root = ../report.tex
\documentclass[report.tex]{subfiles}
% Include in your acknowledgements any person who has made a substantial contribution to your research, but doesn't qualify as an author. Examples include other students, staff, projects or organisations which have provided financial support or data.
% If you have questions about this please get in touch with your supervisor!


\begin{document}

    \begin{acknowledgements}
      % If you have filled out \phdproject and \phdsupervisor in report.tex, you should use the \phdack to acknowledge the PhD project in your research.
        % \phdack\\
        I extend my deepest gratitude to Prof. Dr.-Ing. Sebastian Houben and M.Sc. Santosh Thoduka for their invaluable guidance and unwavering support throughout the course of this research project. Their expertise and insights were crucial in shaping the direction and success of my work.

        Prof. Dr.-Ing. Sebastian Houben's encouragement to pursue thorough research and his strategic guidance have been instrumental in bringing this project to fruition. His ability to inspire and motivate has not only propelled this research forward but has also significantly contributed to my personal and academic growth.

        M.Sc. Santosh Thoduka's hands-on approach and readiness to provide practical solutions to technical challenges have been a cornerstone of my project's progress. His prompt and effective advice in times of difficulty were pivotal in overcoming the numerous challenges encountered during this research.

        The journey from selecting a research topic to transforming it into a successful project was made possible through the combined efforts and continuous support of both my supervisors. Their belief in my capabilities and their assistance up to the very last stages of this project have been a source of great encouragement and learning.

        This experience has imparted not only specific knowledge relevant to this project but has also equipped me with invaluable skills and insights for future research endeavors. I am profoundly thankful for their mentorship and am confident that the lessons learned under their guidance will greatly benefit my future academic pursuits.

        In addition, I would like to express my heartfelt thanks to my family and friends for their constant support and encouragement throughout my project. Their unwavering belief in my potential and their emotional support have been a bedrock of strength during challenging times.

        I would also like to extend my appreciation to my University and particularly to Prof. Dr. Rudolf Berrendorf for granting me access to advanced computational resources. This support was fundamental in addressing the computationally demanding aspects of my research, and their provision of these facilities played a critical role in the successful completion of my project.
    \end{acknowledgements}
\end{document}
